---
title: "Bayesian"
author: "-"
date: "10/14/2019"
output: html_document
---


For the first problem, we'll talk about advertisement on a website
The website owner said: "If you put an ad on our website, your advertisement will be clicked 10% most of the time, but sometimes as low as 5%, sometimes as high as 15%"

Let's say there are 100 daily visitors on each day, if we model it by a binomial distribution (For each visitor, there is a 5%/10%/20% he/she will click the ad). Then the appropiate prior for theta is a continuous distribution that are centered at 10%, and with a chance at 5% and 20%. The range of the distribution must be between 0 and 1

The appropiate model is beta distribution with parameter a and b such that the center is at 10%

```{r}
nrand<-100000
a<-10
b<-90

#We choose the beta such that the mean (a / a+b) is 0.1
dt<-rbeta(nrand,a,b)
plot(density(dt),main='Prior Distribution: beta(10,90)')
```


Here is the sampling distribution for several values of theta
```{r, echo=FALSE}
n<-100 #Number of observations
theta<-c(0.05,0.1, 0.15) #List of possible theta
J<-length(theta) 
prob<-array(dim=c(n,J))
for (j in 1:J){
  for (i in 1:n){
    prob[i,j]<-dbinom(i,n,theta[j])
  }
}

plot(prob[,1],main='Sampling Distribution, n = 100') #First density plot of theta = 0.05
segments(1:n, 0, 1:n, prob[,1])
 
points(prob[,2], col="red") #First density plot of theta = 0.1
segments(1:n, 0, 1:n, prob[,2], col="red")

points(prob[,3], col="blue") #First density plot of theta = 0.2
segments(1:n, 0, 1:n, prob[,3], col="blue")

legend("topright", legend=c("Theta = 0.05", "Theta = 0.1", "Theta = 0.15"),
       col=c("black", "red","blue"), lty=1, cex=0.8, bty="n")

```

Let's say, you have decided that you will take the website offer, and put up and ad there
Next day, from 100 visitor your ad was clicked 30 times

If the prior is a beta(a,b), and the sampling model is a binomial distribution, then the posterior will be
a beta(a+ny,b+n+y)
```{r pressure, echo=FALSE}
#generating a random number from a posterior beta(a + y,b + n + y) distribution

y<-30 #Your ad was clicked 30 times
n<-100 #From 100 visitor
a1<-a+y
b1<-b+n+y

dt.post<-rbeta(nrand,a1,b1)
plot(density(dt.post),main='Posterior: beta(40,220)',
     xlim=c(0, 1))
```

So the true underlying proportion are about 10% ~ 20%

Here is the comparison between the prior and the posterior

```{r}

#Graph overly prior and posterior density

plot(density(dt),xlim=c(0, 1),ylim=c(0,20),main='Prior vs Posterior')
lines(density(dt.post), col="red")

#Add legend
legend("topright", legend=c("Prior", "Posterior"),
       col=c("black", "red"), lty=1, cex=0.8, bty="n")

```